Reproduction frequency and offspring survival decline in elephant seals past prime age

### 2024-10-17 paper/paperv3.qmd
Fixing figure S1

fit_models <- function(a) {
  age_senesce <- a
  sealdat <- sealdat %>% 
    mutate(age_cat = factor(age >= age_senesce, 
                            labels = c("Young", "Old")))

@@

  list(
    h1 = summary(breed_age_mod)$coefficients,
    h2_surv = summary(pup_surv_mod)$coefficients,
    h2_recr = summary(pup_recr_mod)$coefficients,
    h3 = summary(sexrat_age_mod)$coefficients,
    h1_aic = AIC(breed_age_mod),
    h2_surv_aic = AIC(pup_surv_mod),
    h2_recr_aic = AIC(pup_recr_mod),
    h3_aic = AIC(sexrat_age_mod)
  )
}

@@

knitr::kable(p_tbl)
knitr::kable(aic_tbl)

@@

p_tbl %>% 
  pivot_longer(-age_cutoff, names_to = "hypothesis", values_to = "p") %>%
  mutate(hypgrp = ifelse(str_detect(hypothesis, "H3"), 
                         "H3 (sex ratio)", 
                         hypothesis)) %>% 
  ggplot(aes(age_cutoff, p)) +
  geom_point(aes(color = hypothesis == "H3 (sex ratio; 2 tail)")) +
  geom_hline(yintercept = 0.05, linetype = "dashed") +
  geom_text(aes(x, y, label = tag),
            tibble(hypgrp = colnames(p_tbl)[2:5],
                   tag = LETTERS[1:4],
                   x = 8, y = 3),
            vjust = 1,
            fontface = "bold") +
  scale_y_log10(labels = scales::number) +
  scale_color_manual(values = c("black", "grey50")) +
  labs(x = "Senescence onset (years)") +
  expand_limits(y = 3) +
  facet_wrap(~hypgrp) +
  theme(legend.position = "none")

>>>>

fit_models <- function(a) {
  sealdat <- sealdat %>% 
    mutate(age_cat = factor(age >= a, 
                            labels = c("Young", "Old")),
           age10 = (age - a) / 10)

@@

  effect_size <- function(m) {
    probs <- tibble(age = c(15, 19),
                    age_cat = c("Old", "Old")) %>% 
      mutate(age10 = (age - a) / 10) %>% 
      predict(m, re.form = NA, newdata = ., type = "response")
    odds <- probs / (1 - probs)
    odds[2] / odds[1]
  }

  list(
    h1 = summary(breed_age_mod)$coefficients,
    h2_surv = summary(pup_surv_mod)$coefficients,
    h2_recr = summary(pup_recr_mod)$coefficients,
    h3 = summary(sexrat_age_mod)$coefficients,
    h1_aic = AIC(breed_age_mod),
    h2_surv_aic = AIC(pup_surv_mod),
    h2_recr_aic = AIC(pup_recr_mod),
    h3_aic = AIC(sexrat_age_mod),
    h1_effect = effect_size(breed_age_mod),
    h2_surv_effect = effect_size(pup_surv_mod),
    h2_recr_effect = effect_size(pup_recr_mod),
    h3_effect = effect_size(sexrat_age_mod)
  )
}

@@

extract_coef <- function(h) {
  map_dbl(mod_sens, \(m) m[[h]]["age10:age_catOld", "Estimate"])
}
coef_tbl <- tibble(age_cutoff = cutoff, 
                "H1 (breeding)" = extract_coef("h1"),
                "H2a (survival)" = extract_coef("h2_surv"),
                "H2b (recruitment)" = extract_coef("h2_recr"),
                "H3 (sex ratio)" = extract_coef("h3"))

knitr::kable(p_tbl)
knitr::kable(aic_tbl)
knitr::kable(coef_tbl)

@@

left_join(
  pivot_longer(p_tbl, -age_cutoff, names_to = "hypothesis", values_to = "p"),
  pivot_longer(coef_tbl, -age_cutoff, names_to = "hypothesis", values_to = "coef"),
  by = c("age_cutoff", "hypothesis")
  ) %>% 
  left_join(
    pivot_longer(se_tbl, -age_cutoff, names_to = "hypothesis", values_to = "se"),
    by = c("age_cutoff", "hypothesis")
  ) %>% 
  ggplot(aes(age_cutoff, coef)) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_pointrange(aes(size = p, 
                      color = p < 0.05, 
                      ymin = coef - 1.96 * se,
                      ymax = coef + 1.96 * se)) +
  labs(x = "Senescence onset (years)") +
  scale_size_continuous(range = c(0.25, 1)) +
  expand_limits(y = 3) +
  facet_wrap(~hypothesis) +
  theme(legend.position = "none")
